Ownership types in theory and practice (in Rust)

### 2022-11-20 paper.tex
Small additions

\usepackage{booktabs} % For formal tables
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{hyphenat}
\usepackage{todonotes}
\usepackage[babel]{csquotes}

@@

Definition of memory safety\cite{memory1}.
Why memory safery is important\cite{nsa-memory-safety}.

@@

@@

@@

Notes from rust-book\cite{rust-book}.
Ownership definition: set of rules that govern how Rust program manages memory
Compiler checks rules, if violated program doesn't compile
Purpose of Rust ownership is to mainly manage heap data
Ownership rules:
- each value in Rust has an owner
- there can only be one owner at a time
- when the owner goes out of scope, the value will be dropped (value is valid in scope, invalid out of scope)
Definition scope:
```
{                      // s is not valid here, it’s not yet declared
    let s = "hello";   // s is valid from this point forward

    // do stuff with s
}                      // this scope is now over, and s is no longer valid
```

data types of known size at compile time (int, float, bool, char): stored on stack, popped off stack when out of scope, quickly and trivially copied

\subsection{Practical examples using Rust}
% - show common Rust ownership errors
% - Protection against memory vulnerabilitie examples

@@

% Oh, and here goes the summary. Future work is expected in water computers so that programmers can also be productive while swimming.

>>>>

\usepackage{booktabs} % For formal tables
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{hyphenat}
\usepackage{todonotes}
\usepackage[babel]{csquotes}
\usepackage{listings}
\lstset{frame=tb,
  language=Rust,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

@@

% source: Definition of memory safety\cite{memory1}.
% source: Why memory safery is important\cite{nsa-memory-safety}.

@@

 % - TODO: source: Standard ML, C++?

@@

% - source: \cite{understanding-evolving-rust}
% - source: \cite{ownership-types-survey}

@@

% Notes from rust-book\cite{rust-book}.
% Ownership definition: set of rules that govern how Rust program manages memory
% Compiler checks rules, if violated program doesn't compile
% Purpose of Rust ownership is to mainly manage heap data
% Ownership rules:
% - each value in Rust has an owner
% - there can only be one owner at a time
% - when the owner goes out of scope, the value will be dropped (value is valid in scope, invalid out of scope)
% Definition scope:

% \begin{lstlisting}
% {                      // s is not valid here, it’s not yet declared
%     let s = "hello";   // s is valid from this point forward
%     // do stuff with s
% }                      // this scope is now over, and s is no longer valid
% \end{lstlisting}

% data types of known size at compile time (int, float, bool, char): stored on stack, popped off stack when out of scope, quickly and trivially copied

% - TODO: more sources

\subsection{Practical examples using Rust}
% - show common Rust ownership errors
% - Protection against memory vulnerabilitie examples
% - reference: \cite{rust-by-example}

@@
